Evaluation of performances

### 2020-04-30 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

table4 %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )

@@

table4 %>%
  flextable() %>%
  autofit()
```

>>>>

# save to file
table4 %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )

@@

table4 %>%
  print(
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )
```
